https://www.amee.com/
\begin{minipage}{0.5\textwidth}
AMEE UK Limited
13--19 Bevenden Street
London
N1 6AS
\vspace{3em}
\end{minipage}


%\vfill


Dear Sir or Madam,
%Dear Mr...

%I am writing with the pupose of applying for the role of Quantative Analyst at Arrowgrass Capital.
%Considering the experience I gained during my PhD.~,analysing data gathered by the Large Hadron
%Collider, I would be an excellent candidate such a position.

%Working as a member of the LHCb collaboration gave me the opportunity to analyse large datasets,
%working as part of a team or individually.
%I have applied a variety of computational and statistical techniques to these data to search for
%patterns consistent with signatures of phyics processes of interest to a given analysis.
%The nature of this work allowed me to develop my programming abilities, particularly in
%\mbox{\textsc{C\raisebox{0.1em}{{\footnotesize{++}}}}} and Python, which has been furthered by my
%enthusiasm for efficiently solving problems computiationally.

%I am a diligent and self-motivated worker, especially when my work is something that I love.
%The prospect of analysing data exceties me on its own, and the additional insentive of increasing
%profits would only drive me further.

%To work for a hedge fund of your calibre would be a phenomenal opportunity, and I believe that I
%could be an asset to your team.
%Thank you for taking time to consider my application.
%I look forward to hearing from you.

%Please find enclised my CV in application for the role of Quantitative Analyst at Arrowgrass Capital.

I have recenetly been investigating Silicon Roundabout companies with the intetion of getting a job
after I have finished my PhD.
As soon as I read about AMEE I thought how interesting the company sounded

a job, sounded and

During my PhD in high energy physics at Imperial College London I have gained considerable
experience analysing large amounts of data gathered at CERN's Large Hadron Collider.
This background puts me in a position to be a very valuable addition to your company.


As a member of the LHCb experiment,
I have worked with large datasets both individually, and as part of a collaboration, to search for
patterns in data consistent with interesting physics processes.
The techniques applied in such analyses utilise both statistical and computational methods which
would be beneficial to working in the financial sector.
The prospect of applying these skills to look for patterns in different data very exciting to me,
and would enjoy working in a fast-paced intellectual environment.

I firmly believe that I would be an asset to your company, and would embrace the
opportunity to work at Arrowgrass Capital.
Thank you for taking time to consider my application.
I look forward to hearing from you.


%Independend research and as team.
%Initiative.
%Self-motivation.
%Find subject stimulating.

%Fast learner.
%Enjoy learning and appliying new skills.

%I look forward to hearing from you in the future.

%Statistics is an important part...

%analytical thinking
%passion about analysing data with computational techniques
%Modelling of systems


%Utilizing my expertise and drive could be greatly beneficial to your firm.


%Dear Sir or Madam:
Yours Faithfully

%%Dear Mr Name
%Yours sincerely,

Sam Hall


