\section{Profile}
%%%%%%%%%%%%%%%%%

%\cvline{}{Physics, Mathematics, Programming and Data Analysis}
%\cvline{}{Python and C++}

%\cvline{}{}
%{

Data scientist at a predictive analytics firm which is focussed in the retail sector.
Over the past 18 months I have been working on a project with a large UK supermarket, a project
which has been a great success.

I am very technically able, being particularly strong with Python, bash scripting, and SQL.



  Data scientist at Blue Yonder


  Doctoral student at Imperial College London with experience in the analysis of data
  from the LHCb detector, which is located on the Large Hadron Collider.

  Used a variety of computational and statistical techniques to analyse these datasets.

  Motivated by the idea of applying my programming skills to
  solve diverse problems in a fast-paced, creative environment with large datasets.

  My ideal career would be in the sphere of data science, since my skill set is similar and
  the subject interests me deeply.

  Good work ethic, problem solving skills, quick at adapting to new problems working as part of a
  team or independently.


  Motivation


  Team

  %quaick at adapting
  %team or independently
  %\begin{itemize}
    %\item Problem solving
    %\item Quick to pick up new software and programming languages
    %\item team / independently
  %\end{itemize}
%}
%\cvline{Programming and Software Development}{Python and C++}
%{
  %\begin{itemize}
    %\item EvtGen
  %\end{itemize}
%}
















