%https://www.mi5.gov.uk/careers/graduate-careers/intelligence-and-data-analyst-development-programme.aspx

\begin{minipage}{0.5\textwidth}
%http://www.gresearch.co.uk/contact
G-Research,\\
Whittington House,\\
19--30 Alfred Place,\\
London,\\
WC1E 7EA\\
%0207 631 7500
\vspace{3em}
\end{minipage}


Dear Sir or Madam,
%Dear Mr...

Please find attached my CV in application for the role of Quantitative Analyst at G-Research.
During my PhD in high energy physics at Imperial College London I have gained considerable
experience analysing large amounts of data gathered at CERN's Large Hadron Collider.
This background puts me in a position to be a very valuable addition to your company.


As a member of the LHCb experiment,
I have worked with large datasets both individually, and as part of a collaboration, to search for
patterns in data consistent with interesting physics processes.
The techniques applied in such analyses utilise both statistical and computational methods which
would be beneficial to working in the financial sector.
The prospect of applying these skills to look for patterns in different data very exciting to me,
and would enjoy working in a fast-paced intellectual environment.

I firmly believe that I would be an asset to your high calibre team, and would embrace the
opportunity to work at G-Research.
Thank you for taking time to consider my application.
I look forward to hearing from you.

%Dear Sir or Madam:
Yours Faithfully

%%Dear Mr Name
%Yours sincerely,

Sam Hall


