
Arrowgrass Capital Partners LLP.\\
10 Portman Square, Floor 3,\\
Marylebone,\\
London,\\
W1H 6AZ\\

%Tel +44 (0) 203 100 1000

\vfill


Dear Sir or Madam,
%Dear Mr...

%I am writing with the pupose of applying for the role of Quantative Analyst at Arrowgrass Capital.
%Considering the experience I gained during my PhD.~,analysing data gathered by the Large Hadron
%Collider, I would be an excellent candidate such a position.

%Working as a member of the LHCb collaboration gave me the opportunity to analyse large datasets,
%working as part of a team or individually.
%I have applied a variety of computational and statistical techniques to these data to search for
%patterns consistent with signatures of phyics processes of interest to a given analysis.
%The nature of this work allowed me to develop my programming abilities, particularly in
%\mbox{\textsc{C\raisebox{0.1em}{{\footnotesize{++}}}}} and Python, which has been furthered by my
%enthusiasm for efficiently solving problems computiationally.

%I am a diligent and self-motivated worker, especially when my work is something that I love.
%The prospect of analysing data exceties me on its own, and the additional insentive of increasing
%profits would only drive me further.

%To work for a hedge fund of your calibre would be a phenomenal opportunity, and I believe that I
%could be an asset to your team.
%Thank you for taking time to consider my application.
%I look forward to hearing from you.

I enclose my CV in application for the role of Quantitative Analyst at Arrowgrass Capital.
During my PhD.~in high energy physics I have gained considerable experience analysing data gathered
by the Large Hadron Collider using both statistical and computational methods.
This background puts me in an excellent position to be a valuable addition to your team.

As a member of the LHCb collaboration, I have worked with large datasets both individually and as
part of a team.
I have used a variety of computational and statistical techniques to search for patterns consistent
with various physics signatures of interest, developing my programming skills, particularly in
\mbox{\textsc{C\raisebox{0.1em}{{\footnotesize{++}}}}} and Python.
The prospect of using these skills to solve problems efficiently and effectively in excites me,
especially the idea of applying them to analyse a different kind of data in an a fast
paced, intellectual environment.
%I am driven and self-motivated and very excited to analyse a different kind of data in an a fast
%paced, intellectual environment.

I firmly believe that I would be an asset to your high calibre team, and would embrace the
opportunity to work at Arrowgrass Capital.
Thank you for taking time to consider my application.
I look forward to hearing from you.


%Independend research and as team.
%Initiative.
%Self-motivation.
%Find subject stimulating.

%Fast learner.
%Enjoy learning and appliying new skills.

%I look forward to hearing from you in the future.

%Statistics is an important part...

%analytical thinking
%passion about analysing data with computational techniques
%Modelling of systems


%Utilizing my expertise and drive could be greatly beneficial to your firm.


%Dear Sir or Madam:
Yours sincerely,

%%Dear Mr Name
%Yours Failthfully

Sam Hall


